The Blue Obelisk five years on

### 2011-03-02 paper.tex
Initial start on software table

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - Sample table title}
    Here is an example of a \emph{small} table in \LaTeX\ using  
    \verb|\tabular{...}|. This is where the description of the table 
    should go. \par \mbox{}
    \par
    \mbox{
      \begin{tabular}{|c|c|c|}
        \hline \multicolumn{3}{|c|}{My Table}\\ \hline
        A1 & B2  & C3 \\ \hline
        A2 & ... & .. \\ \hline
        A3 & ..  & .  \\ \hline
      \end{tabular}
      }
  \subsection*{Table 2 - Sample table title}
    Large tables are attached as separate files but should
    still be described here.

>>>>

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - Blue Obelisk Open Source software projects}
    (Description if necessary XXXXXXXXXXXXXXX. Add citations to project names.)
    \par \mbox{}
    \par
    \mbox{
      \begin{tabular}{|c|c|c|}
        %% \hline \multicolumn{3}{|c|}{My Table}\\ \hline
        \hline Name & Website & Description? or Lead Developer? \\ \hline
        \multicolumn{3}{|c|}{Cheminformatics toolkits} \\ \hline
        Chemistry Development Kit & http://cdk.sf.net & XXXX  \\ \hline
        Open Babel & http://openbabel.org & Geoffrey Hutchison et al \\ \hline
        A2 & ... & .. \\ \hline
        A3 & ..  & .  \\ \hline
      \end{tabular}
      }
  \subsection*{Table 2 - Sample table title}
    Large tables are attached as separate files but should
    still be described here.
